---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r, cache=TRUE}
data.url <- 'https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip'
data.zipfile <- './activity.monitoring.data.zip'
download.file(data.url, data.zipfile)
unzip(data.zipfile)
steps.data <- read.csv('activity.csv', header = TRUE)
steps.data$date <- as.Date(steps.data$date)
head(steps.data)
```
## What is mean total number of steps taken per day?
```{r}
library(dplyr)
steps.daily.total <- steps.data %>% 
    group_by(date) %>% 
    summarise(steps_total = sum(steps, na.rm = TRUE))

hist(steps.daily.total$steps_total, 
     main='Total steps taken per day',
     xlab = 'Total steps per day',
     breaks = seq(0, 25000, by = 1000),
     col = 'green')

```

The mean of total number of steps taken per day
```{r}
mean(steps.daily.total$steps_total)
```

The median of totla number of steps taken per day
```{r}
median(steps.daily.total$steps_total)

```

## What is the average daily activity pattern?
1. Make a time series plot (i.e. type="l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r}
## calculate average number of steps on each 5-minute interval
steps.interval.average <- steps.data %>% 
    group_by(interval) %>% 
    summarise(steps_mean = mean(steps, na.rm = TRUE))
  
## plot a line chat 
plot(x = steps.interval.average$interval,
     y = steps.interval.average$steps_mean,
     main = 'Average Daily Activity Pattern',
     xlab = '5-minute intervals',
     ylab = 'Average Steps Taken Daily',
     col = 'green',
     type = 'l')
```

2. Report which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps
```{r}
max.steps <- steps.interval.average$interval[which.max(steps.interval.average$steps_mean)]
max.steps

```


## Imputing missing values

1. Calculate and report the total number of missing values in the dataset.
```{r}
sum(is.na(steps.data$steps))
```

2. Devise a strategy for filling in all of the missing values in the dataset.
```{r}

```

3. Create a new dataset that is equal to the original dataset but with the missing data filled in.
```{r}

```

4. Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day.
```{r}

```

## Are there differences in activity patterns between weekdays and weekends?

```{r}

```
